A comparison of approaches to Kazakh to Kyrgyz machine translation

### 2015-02-18 2015-eamt-kazkir/2015-eamt-kazkir.tex
fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59005 72bbbca6-d526-0410-a7d9-f06f51895060

\author{
  Jonathan North Washington\\
  Departments of Linguistics\\
  and Central Eurasian Studies\\
  Indiana University\\
  Bloomington, Indiana 47405 USA\\
  \texttt{jonwashi@indiana.edu}  \And
  \textbf{Francis M. Tyers}\\
  HSL-fakultetet\\ 
  UiT Norgga\'{a}rktala\v{s} universitehta \\
  9017 Romsa, Norway \\
  {\tt francis.tyers@uit.no}
}

@@

Within the Apertium project, work on several MT systems between Turkic languages has been started (Turkish--Kyrgyz, Azeri--Turkish, Tatar--Bashkir), but the Kazakh--Tatar system described by the present study is the closest to production-ready of them.  Among these systems is a prototype Tatar--Bashkir machine translation system \citep{tyerswashingtonsalimzyanbattalov12}; due to the closeness of these languages, it proved to provide high accuracy in its translations, but being a prototype system by design, had relatively low coverage.

@@

>>>>

\author{
  Jonathan North Washington\\
  Departments of Linguistics\\
  and Central Eurasian Studies\\
  Indiana University\\
  Bloomington, Indiana 47405 USA\\
  \texttt{jonwashi@indiana.edu}  \And
  \textbf{Francis M. Tyers}\\
  HSL-fakultetet\\ 
  UiT Norgga \'{a}rktala\v{s} universitehta \\
  9017 Romsa, Norway \\
  {\tt francis.tyers@uit.no}
}

@@

Within the Apertium project, work on several MT systems between Turkic languages has been started (Kazakh--Tatar, Tatar--Bashkir, Turkish--Kyrgyz, and Azeri--Turkish).  There are two published works describing these systems, the first is \cite{tyerswashingtonsalimzyanbattalov12} which describes a Tatar--Bashkir machine translation system; due to the closeness of these languages, it proved to provide high accuracy in its translations, but being a prototype system by design, had relatively low coverage. The second is \cite{tyerswashingtonsalimzyan13} which describes a high-coverage Kazakh--Tatar system.

@@

\section*{Acknowledgements}

\emph{Anonymised for review}
